
Using v 1.0.1 (March 30)

leave "fields" out of important examples (since they are really only
a partial algebra).

p5. near bottom: ph.d. capitalize ?

p6: "it is well to note" shouldn't this be "good"

p8: change Pudlakand (twice)

p10: near the top: you have L embedded into L' \le Eq(X), but don't
     you want L isomorphic to L'

I skipped section 2.3 and 2.4.

Using v 20120331

Section 3.2, just after the picture: "Since L ... is representable". Maybe
"concretely represented" or closed.

Ch 4, second paragraph: "Partially order the set X" do you mean totally
order X? What if X is an antichain.

Section 4.1 well-known shoule be well known

Usually Figure captions come at the bottom of the figure So `
unless the the thesis police requite it, you should put them at the bottom.

Lemma 5.2.1 is Thm 3.4 of ALVI, and is pretty standard. I suggest 
you just quote that.

Using 20120409

Chapter 4:
In definitions you should nave "iff"---just "if". Also many people 
object to the abreviation "iff". Neither of these are pressing issues.

the second line before section 4.1.1, lambda sub h, should h be capital?

p 41 near the bottom (in the Examples subsection) "the class
of subdirectly irreducible lattices" Should lattices be groups.

4/13/2012

In ch 5 "eachother" should be two words.

page 63, top say M_2 has exactly 2 maximal subgroups of its own is not true:
it might have others not above H.

page 63, the forst displayed equation has one J_1 in it which should be J_2.

4/14/2012

on page 65, case 1 of the proof, besided H < X < G, you need X \ne M_2.

  case 2, you have "The conclusion is N \cap J_1  is normal in G"
          This is correct. Since J_1 is core free, you can immediately 
          conclude that N \cap J_1 = 1.











